Security Metrics for the Android Ecosystem

### 2015-07-27 dastats.tex
./update.sh

\newcommand{\daEndDate}{2015-07-15}

@@

\newcommand{\daUpdatednessNominal}{0.0521}
\newcommand{\daUpdatedness}{$0.0521 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.21\%}
\newcommand{\daUpdatednessPerc}{$5.21 \pm 0.0\%$}

@@

\newcommand{\daCurrentMeanInsecurityPercNominal}{79.6\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$79.6 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{80\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$80 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{20.4\%}
\newcommand{\daCurrentMeanSecurityPerc}{$20.4 \pm 0.1\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{20\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$20 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.204}
\newcommand{\daCurrentVulnFree}{$0.204 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.123 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0536}
\newcommand{\daCurrentUpdatedness}{$0.0536 \pm 0.0$}
\newcommand{\daCurrentUpdatednessPercNominal}{5.36\%}
\newcommand{\daCurrentUpdatednessPerc}{$5.36 \pm 0.0\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{5.4\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$5.4 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.79}
\newcommand{\daCurrentSecurityScore}{$3.79 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{898}
\newcommand{\daDailyParticipation}{$898 \pm 245$}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{327}
\newcommand{\daOSCurveHalfDeployed}{$327 \pm 91$}

@@

\newcommand{\daOSCurveFullDeployedNominal}{1\,130}
\newcommand{\daOSCurveFullDeployed}{$1\,130 \pm 260\,000$}
\newcommand{\daAPICurveFitParamFirst}{99.7}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.71 \pm 0.04$ \\  Nexus 4 & $0.30 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.69 \pm 0.04$ \\  Nexus 7 & $0.26 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.24 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.53 \pm 0.00$ & $3.03 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.27 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.03 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.52 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.27 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.87 \pm 0.03$ \\  T-Mobile & $0.22 \pm 0.00$ & $0.18 \pm 0.00$ & $0.40 \pm 0.01$ & $3.81 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.65 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.42 \pm 0.03$ \\  3 & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.39 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.17 \pm 0.04$ \\  AT\&T & $0.14 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.13 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.84 \pm 0.01$ & $2.88 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.84 \pm 0.02$ \\  n Telenor & $0.04 \pm 0.00$ & $0.12 \pm 0.00$ & $1.21 \pm 0.02$ & $1.89 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.47 \pm 0.03$ & $1.41 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $1.88 \pm 0.02$ & $0.94 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.07 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.55 \pm 0.04$ & $0.55 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.548}
\newcommand{\daSecScoreWorstoperatorScore}{$0.548 \pm 0.018$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{74}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$f$ & 0.4 & 0.667 & 0.5 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.667 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.276$ & $-0.0991 \pm 0.32$ & $-0.462 \pm 0.167$ & $-0.488 \pm 0.216$ \\equal & $-0.108 \pm 0.062$ & $-0.0368 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0608 \pm 0.122$ & $-0.0112 \pm 0.232$ & $0.0238 \pm 0.0807$ & $-0.00602 \pm 0.12$ \\$u$ & $0.367 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.976 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.40$ & $1.48 \pm 0.29$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.123}

@@

>>>>

\newcommand{\daEndDate}{2015-07-19}

@@

\newcommand{\daUpdatednessNominal}{0.0523}
\newcommand{\daUpdatedness}{$0.0523 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.23\%}
\newcommand{\daUpdatednessPerc}{$5.23 \pm 0.0\%$}

@@

\newcommand{\daCurrentMeanInsecurityPercNominal}{79.5\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$79.5 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{79\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$79 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{20.5\%}
\newcommand{\daCurrentMeanSecurityPerc}{$20.5 \pm 0.2\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{21\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$21 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.205}
\newcommand{\daCurrentVulnFree}{$0.205 \pm 0.002$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.119 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0561}
\newcommand{\daCurrentUpdatedness}{$0.0561 \pm 0.0016$}
\newcommand{\daCurrentUpdatednessPercNominal}{5.61\%}
\newcommand{\daCurrentUpdatednessPerc}{$5.61 \pm 0.16\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{5.6\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$5.6 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.81}
\newcommand{\daCurrentSecurityScore}{$3.81 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{896}
\newcommand{\daDailyParticipation}{$896 \pm 249$}

@@

\newcommand{\daOSCurveHalfDeployedNominal}{328}
\newcommand{\daOSCurveHalfDeployed}{$328 \pm 91$}

@@

\newcommand{\daOSCurveFullDeployedNominal}{1\,140}
\newcommand{\daOSCurveFullDeployed}{$1\,140 \pm 260\,000$}
\newcommand{\daAPICurveFitParamFirst}{99.4}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.71 \pm 0.04$ \\  Nexus 4 & $0.30 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.69 \pm 0.04$ \\  Nexus 7 & $0.26 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.25 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.53 \pm 0.00$ & $3.03 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.27 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.03 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.52 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.27 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.87 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.40 \pm 0.01$ & $3.81 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.65 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.42 \pm 0.03$ \\  3 & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.39 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.17 \pm 0.04$ \\  AT\&T & $0.14 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.13 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.84 \pm 0.01$ & $2.88 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.84 \pm 0.02$ \\  n Telenor & $0.04 \pm 0.00$ & $0.12 \pm 0.00$ & $1.21 \pm 0.02$ & $1.89 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.47 \pm 0.03$ & $1.41 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $1.88 \pm 0.02$ & $0.94 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.07 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.03 \pm 0.00$ & $2.56 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.536}
\newcommand{\daSecScoreWorstoperatorScore}{$0.536 \pm 0.018$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{73}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\$f$ & 0.4 & 0.667 & 0.5 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.277$ & $-0.0991 \pm 0.321$ & $-0.461 \pm 0.167$ & $-0.488 \pm 0.217$ \\equal & $-0.108 \pm 0.062$ & $-0.0367 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0608 \pm 0.122$ & $-0.0112 \pm 0.232$ & $0.0242 \pm 0.0808$ & $-0.00596 \pm 0.12$ \\$u$ & $0.367 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.975 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.41$ & $1.48 \pm 0.3$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.119}

@@

\newcommand{\daTabSpearmanRanks}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ $\pm\sigma$ & 0.211 & 0.169 & 0.175 & 0.632 \\ \hline $u$ & 0.297 & 0.804 & 0.618 & 1.0 \\$m$ & 0.794 & 0.593 & 0.969 & -1.0 \\$f$ & 0.83 & 0.775 & 0.934 & 1.0 \\weight $u$ & 0.939 & 0.996 & 0.991 & 1.0 \\weight $m$ & 0.976 & 0.964 & 0.996 & 1.0 \\equal & 1.0 & 0.996 & 1.0 & 1.0 \\\end{tabular} \caption{Spearman Rank correlation coefficients for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daStartDateMonth}{July 2011}
\newcommand{\daEndDateMonth}{July 2015}
\newcommand{\daSecScoreBestsummary}{nexus}
\newcommand{\daSecScoreBestsummaryScoreNominal}{5.17}
\newcommand{\daSecScoreBestsummaryScore}{$5.17 \pm 0.0$}
\newcommand{\daSecScoreBestsummaryNumFullVersions}{92}
\newcommand{\daSecScoreWorstsummary}{notnexus}
\newcommand{\daSecScoreWorstsummaryScoreNominal}{2.7}
\newcommand{\daSecScoreWorstsummaryScore}{$2.7 \pm 0.0$}
\newcommand{\daSecScoreWorstsummaryNumFullVersions}{1\,250}
